### 2017-12-06 Docs/Thesis/docs/chapter1.tex
merge brench

Emerging technologies such as SDN and NFV are great promises. If succeeding at large-scale, they would change drastically the development and operation of computer networks. However, its enabling technologies such as virtualization still pose challenges on performance,  reliability, and security\cite{nfv-challenges}. Closed hardware solutions are easier to pass on Service Layer Agreement since they have a much more predictable behavior. Since it is expected virtualization to impact negatively on performance, these VNFs have to keep its degradation as small as possible. Guarantee the Service Layer Agreements on emerging scenarios is now a harder question. There is a demand for more reliable methods to ensure the SLAs, over different types of loads.

@@

Realistic workload generators are also essential security research\cite{ditg-paper}.  Generation of realistic workloads is important in the evaluation of firewall middleboxes. It includes studies of intrusion, anomaly detection, and malicious workloads\cite{ditg-paper}.

Since on traditional hardware-based types of \textit{middleboxes}, the impact of realistic traffic is not negligible; we can expect that its impact over virtualized middle-boxes should be even larger, due the extra overhead of a virtualization layer.

Another critical point is the flow-oriented operation of SDN networks. Each new flow arriving on an SDN switch demands an extra communication load between it and the controller. This may create a bottleneck between the switch and the controller.  Also the SDN switches have a flow-oriented operation. Since its operation relies on queries on flow tables, a stress load must have the same flow properties of an actual Internet Service Provider.

Therefore, there is a demand for the study of the impact of a realistic traffic on this new sort of environment. How VNFs and virtualized middle-boxes and SDN testbeds will behave if stressed with a realistic traffic load in comparison to a constant rate traffic is a relevant subject.

@@

Therefore we have a large variety open-source tools available for custom traffic generation. But reproducing a realistic traffic scenario is a hard question. Selecting the right framework, a good traffic model, and the right configuration, is by itself a complex research project\cite{legotg-paper}\cite{selfsimilar-ethernet}. But usually this is not the goal of the project, so the researcher or the them have scarce time available to work over it. Since it is usually is not the main goal of the project, but just a mean many times a simplistic and irrealistic sollution is opt because of the limited resources such as time and manpower.   Reproducig a realistic traffic usung these tools is a manual process and demands implementation of scripts or programs leveraging human (and scarce) expertise on network traffic characteristics  and experimental evaluation. Since it usually is not the goal of the research, but a mean.

For this gap, there are some sollutions on the open source community. Tools like Swing and Harpoon uses capture traces to set intern parameters, enabling an easier configuration. Also, Swing uses complex multi-levels models which are able to provide a high degree of realism\cite{swing-paper}. But they have their issues as well. Harpoon does not configure parameters at packet level\cite{harpoon-paper} and is not supported by newer Linux kernels, what may be a huge problem with setup and configuration. Swing\cite{swing-paper} aims to generate realistic traffic, but focous on background traffic, and high throughputs it is not a goal off the application\cite{swing-paper} \cite{legotg-paper}. Due the fact that its traffic generation engine is coupled to its modeling framework, you can't opt to use a newer/faster packet generation library. The only way of replacing the traffic engine is changing and recompiling the original code. This is clearly a hard task\cite{legotg-paper}, and an error prone activity. Again, we fall in the same problem a complex task that usually is not the goal of the project.

@@

\section{\textit{SIMITAR}: SnIffing, ModellIng and TrAffic geneRation}

\begin{figure*}[ht!]
        \centering
        \includegraphics[height=2.4in]{figures/ch1/layer-diagram}
        \caption{ Architecture conceptual idea: a toll to automatize many tasks on traffic modelling and generation.}
    \label{fig:layer-diagram}
\end{figure*}

In this section, we are going to present our solution discussed in this text. SIMITAR is a traffic generator able to learn features of a real traffic automatically, and reproduce a synthetic traffic similar to the original. It records a model for the traffic in an XML file we call Compact Trace Descriptor.

But first we will formalize our research targets, and then define a requirement list for SIMITAR, that means, what we want it to do. The main research targets are:

@@

We call our  tool \textit{SIMITAR}, an acronym for \textit{SnIffing, ModellIng and TrAffic geneRation}.  This acronym summarizes its operation. Now, we are going to define a requirement list for our proposed software.

@@

	\item It must be able to extract data from a real traffic and store in a database. It must be able to obtain data from real-time traffics and from \textit{pcap} files;

	\item It must have a flow-based abstract model for traffic generation, not attached to any specific technology. Then, its model should be parameterized using this stored data;

@@

	\item Easy expansion: the traffic modeling and generation must be decoupled. Ideally, it must able to use as traffic generator engine any library or traffic generator tool;

	\item Easy to use: It must be simple to use. It has to take as input a Compact Trace Descriptor, just as a traffic replay engine (such as TCPreplay) would take a \textit{pcap} file;

	\item Traffic programmability: It must have what we call \textit{traffic generation progamability}. The compact trace descriptor must be simple and easy to read. In that way, the user may want to create his custom traffic, in a platform agnostic way. The traffic programmability must be flow-oriented;

	\item The traffic modeling and generation must be flow-oriented. Each flow must be modeled and generated separately.

@@

On the figure ~\ref{fig:layer-diagram} we abstract our concepts we stated in a layer diagram model. Or tool must work as an interface for the user automatizing traffic modeling, configuration, and emulation. Also should provide a service intelligence, programmability, and acceleration\footnote{Packet acceleration is a concept introduced by DPDK\cite{web-dpdk}, which means kernel by-pass. Packet acceleration optimizes the packet processing, and therefore traffic generation, enabling higher throughput rates. But, in the current version, this feature is not implemented, but its methodology is discussed in the section of future works in the chapter ~\ref{ch:conclusion}.}.

Our primary goal is to offer simple configuration, with realism, at a reasonable speed. To do this, we are introducing the concept of programmability for traffic generation. With SIMITAR, the user may program its synthetic traffic in a platform agnostic way. The intermediate layer of the figure ~\ref{fig:layer-diagram} summarize, the goal of the project in an illustrative way.

Instead of storing a huge file \textit{pcap} with a size of many \textit{gigas}, we create a light-weight set of models and parameters that describe this same trace. This tool will store the generalized set of parameters in a human and machine-readable XML file we call \textit{Compact Trace Descriptor} (\textit{CTD}). Then, we use this data as input for a traffic generator engine. We do so using APIs or creating new processes in a controlled manner. So will be possible to control packet parameters and flow's behavior in an automatized and self-configuring way.

Using a component methodology, we decouple the traffic generation, from the data collection and parameterization process. Building it in this non-monolithic way,  enable a simple port for different traffic generators engines, what make our tools easy for updating with newer technologies. A project guideline is to reuse as much code and components as possible from the open-source community.

>>>>

Emerging technologies such as SDN and NFV are great promises and would change drastically the development and operation of computer networks. However, its enabling technologies such as virtualization still pose challenges on performance,  reliability, and security\cite{nfv-challenges}. Closed hardware solutions are easier to pass on Service Layer Agreement since they have a much more predictable behavior. Since it is expected virtualization to impact negatively on performance, these VNFs have to keep its degradation as small as possible. Guarantee the Service Layer Agreements on emerging scenarios is now a harder question. There is a demand for more reliable methods to ensure the SLAs, over different types of loads.

@@

Realistic workload generators are also essential security research\cite{ditg-paper}.  Generation of realistic workloads is important in the evaluation of firewall middleboxes. It includes studies of intrusion, anomaly detection, and malicious workloads\cite{ditg-paper}. Since on traditional hardware-based types of \textit{middleboxes}, the impact of realistic traffic is not negligible; we can expect that its impact over virtualized middle-boxes should be even larger, due the extra overhead of a virtualization layer.

Another critical point is the flow-oriented operation of SDN networks. Each new flow arriving on an SDN switch demands an extra communication load between it and the controller. This may create a bottleneck between the switch and the controller.  Also the SDN switches have a flow-oriented operation. Since its operation relies on queries on flow tables, a stress load must have the same flow properties of an actual Internet Service Provider. Therefore, there is a demand for the study of the impact of a realistic traffic on this new sort of environment. How VNFs and virtualized middle-boxes and SDN testbeds will behave if stressed with a realistic traffic load in comparison to a constant rate traffic is a relevant subject.

@@

We have a large variety open-source tools available for custom traffic generation, but reproducing a realistic traffic scenario is a hard question. Selecting the right framework, a good traffic model, and the right configuration, is by itself a complex research project\cite{legotg-paper}\cite{selfsimilar-ethernet}. Since it is usually is not the main goal of the project, but just a mean, many times a simplistic and irrealistic sollution is opt because of the limited resources such as time and manpower.  Reproducig a realistic traffic usung these tools is a manual process and demands implementation of scripts or programs leveraging human (and scarce) expertise on network traffic characteristics  and experimental evaluation.

There are fewer sollutions on the open source community available that aim to fill this gap. Tools like Swing and Harpoon uses capture traces to set intern parameters, enabling an easier configuration. Also, Swing uses complex multi-levels models which are able to provide a high degree of realism\cite{swing-paper}. However they have their issues as well. Harpoon does not configure parameters at packet level\cite{harpoon-paper} and is not supported by newer Linux kernels, what may be a huge problem with setup and configuration. Swing\cite{swing-paper} aims to generate realistic traffic, but focous on background traffic, and high throughputs it is not a goal off the application\cite{swing-paper} \cite{legotg-paper}. Due the fact that its traffic generation engine is coupled to its modeling framework, you can't opt to use a newer/faster packet generation library. The only way of replacing the traffic engine is changing and recompiling the original code. This is clearly a hard task\cite{legotg-paper}, and an error prone activity. Again, we fall in the same problem a complex task that usually is not the goal of the project.

@@

\section{Problem Statement}

Based on what we stated,  we are going to formalize our research targets, and define que requet list to fulfill these gaps. Our main research targets in this work are:

@@

Hence, we will define a requeriment list for the tool we are going to develop and present in this research:

@@

	\item Autoconfigurable: It must be able to extract data from a real traffic and store in a database, and use it to parametrize its traffic model. It must be able to obtain data from real-time traffics and from \textit{pcap} files;

	\item Technology independent: It must have a flow-based abstract model for traffic generation, not attached to any specific technology.

@@

	\item Extensibility: the traffic modeling and generation must be decoupled. Ideally, it must able to use as traffic generator engine any library or traffic generator tool;

	\item Simple usage: It must be easy to use. It has to take as input a Compact Trace Descriptor, just as a traffic replay engine (such as TCPreplay) would take a \textit{pcap} file;

	\item Traffic generation programmability: It must have what we call \textit{traffic generation progamability}. The compact trace descriptor must be simple and easy to read. In that way, the user may want to create his custom traffic, in a platform agnostic way. The traffic programmability must be flow-oriented;

	\item Flow-oriented: The traffic modeling and generation must be flow-oriented. Each flow must be modeled and generated separately.

@@
